	\documentclass [french]{paper}
	\usepackage[francais]{babel}
	\usepackage[utf8]{inputenc}
	\usepackage{graphicx}
	\usepackage{color}
	
	\begin{document}
		
	We recall that the purpose of this study is to verify the positive impact of complementarity on collaborative negotiation between an agent and a human user.
	
	\section{Hypotheses}
	\begin{itemize}
		\item Dyads of complementary dominance achieve high joint gain compared to the other dyads.
		\item Participants feel more comfortable with an agent displaying a complementary behavior.
		\item Complementarity increases the liking between the negotiators.
	\end{itemize}
			
	\section{Conditions}
		We have formulated three conditions to evaluate our model of negotiation based on the relation of dominance:
			\begin{itemize}
			\item Complementary Behavior: The agent will adapt its behavior to complement the user's dominance behavior
			
			\item Similar behavior: The agent will behave similarly to the user. In a way it will mimic the dominance strategy expressed by the user
			
			\item Condition of control: Agent who does not adapt its behavior. Its power will be initiated at $ pow = 0.5 $ to express a neutral behavior.
		\end{itemize}
		
		
	\section{Method}
		The experiment in which you will participate aims to analyze the behavior of conversational agents in the context of negotiation dialogues with  humans.
		
		As part of this study, you will interact with one or several conversational agents.
		
		Imagine that you are having dinner with a friend tonight.You need to discuss with him so as to choose a restaurant that suits you both.
		
		The choice of a restaurant is based on your personal preferences. We will take into account 4 criteria. You'll take into account the type of \textbf {cuisine}, \textbf {the price}, \textbf {the atmosphere} and \textbf {the location} to choose a restaurant. For example the restaurant Barocco is defined with the criteria presented in the table \ref{teb:exEn}
		
			\begin{table}[h]
		\begin{tabular} {|c|c|c|c|c|}
			\hline
			Restaurant name & cuisine & Price & Atmosphere & location \\
			\hline
			Borocco & Italian & Expensive & Calm & River side \\
			\hline 
		\end{tabular}
		\label{teb:exEn}
		\caption{Presentation of the restaurant Borocco}
	\end{table}
	
	The study will take place in three stages:
	
	First, you will do a training session to get familiar with the interaction interface.
	
	Then, for the purposes of the study, we will ask you to fill in your preferences for each criterion.  Note that the agents you are going to interact with do not know your preferences. They will be used to analyze the dialogues. Please, respect the preferences that you would have communicated to us during the interactions.
	
	Finally, you will discuss with three different people represented by conversational agents. Please, behave \textbf{naturally} with each of the three agents, as you would have done with one of your relations to choose a restaurant.
	If you have any question, its time to ask the experimenter. Otherwise, we can start the first stage of the study.
	\section{Informations about the preferences}
		\subsection{Welcome screen}
	
		For the purposes of this study, we ask you to enter your preferences for each criterion that will be discussed during the negotiation.
		
		Since the criteria are independent, each criterion will be presented independently of the others. You have to focus your rank only on the criterion presented and ignore the other criteria.
		
		We invite you to rank your preferences in an \textbf {descending} order, starting with the value you like the most,  to the value you like the least.
		
		If you have any question, you can call the experimenter. Otherwise, we can start the study.
	
			 
			\textbf{Message to print for each criterion:}  All other things being equal,sort the following values in ascending order of your preferences.
	
		
		\section{Questionnaire}
			For each agent, ask the following questions. The word "agent" will be replaced with the name that we will attribute to the agent.
			\begin{enumerate}
			% We need to evaluate the perception of the value creation 
			\item I'm satisfied with the final choice
			\item The final choice was fair for the agent.
			%	\item The final choice was fair 
			% manipulation check question
			\item Cuisine was the first criterion you agreed on 
			\item  We both agreed to go a cheap restaurant.
			
			% Evaluate the liking during the negotiation
			
			\item I liked negotiating with the agent
			\item I thought that the agent was popular.
			
			% Evaluate the compfort in the negotiation
			\item I felt comfortable during the negotiation process.
			\item I found that the interaction was comfortable
			\item I felt relaxed during the negotiation
			\item I felt anxious during the negotiation
			
			
			
			
			\item how comfortable the participant was describing the pictures
			\item how comfortable the participant found the interaction
			\item the degree to which the participant felt relaxed during the task
			\item he reverse of the degree to which the participant	felt anxious during the task
			%				\item I appreciated negotiating with the agent.
			%				\item I enjoyed discussing with the agent.
			%				\item I disliked negotiating with the agent. 
			%				\item The agent was unpleasant during the negotiation
			
			
			
			
			% Evaluate behaviors of dominance during the negotiation
			\item The agent took into account my preferences.
			\item The agent pressed its position during the negotiation.
			\item The agent gave up his position during the negotiation
			\item The agent made concessions during the negotiation.
			\item The agent took the lead the negotiation.
			\item The agent was self-centered.
			\item The agent takes the initiative in the negotiation.
			\item The agent was demanding
			
			\item I have the tendency to take the lead the negotiation.
			\item I took into account the preferences of the agent.
			\item I gave up my position during the negotiation
			\item I pressed my position during the negotiation.
			\item I was self-centered during the negotiation.
			\item I made concessions during the negotiation.
			\item I took the initiative during the negotiation
			\item I was demanding
			
				
		\end{enumerate}
		
% ------------------------ Version FR ----------------------
\section{Version FR}
	Nous rappelons que le but de cet étude est de vérifier l'impact positif de la complémentarité sur la négociation collaborative entre un agent et un utilisateur humain. 
	
	\subsection{conditions}
	
	Nous avons formulé trois conditions pour l'évaluation de notre modèle de négociation basé sur la relation de dominance: 
	\begin{itemize}
		\item Comportement complémentaire: L'agent va adapter son comportement pour complémenter le comportement de dominance de l'utilisateur
		
		\item Comportement similaire: L'agent va adopter un comportement similaire à celui de l'utilisateur. D'une manière il va imiter la stratégie de dominance exprimé par l'utilisateur
		
		\item Condition de contrôle : Agent qui ne s'adapte pas dont le pouvoir sera initié à $pow =0.5$. Un comportement neutre. 
		\end{itemize}
		
		
			\subsection{Explication de l'étude}
			\textbf{ Version FR}
			
			Bonjour, l’expérimentation à laquelle vous allez participer à pour objectif d'analyser les comportements d’un agent conversationnel dans le cadre d’un dialogue de négociation avec un humain.
			Dans le cadre de cette étude, vous allez dialoguer avec un ou plusieurs agents conversationnels.
			
			Imaginez que vous allez dîner avec un ami ce soir. Vous allez discuter avec lui afin de choisir un restaurant qui vous convienne à tous les deux.
			
			Le choix d'un restaurant est basé sur vos préférences personnelles. Nous allons prendre en compte 4 critères: le type de \textbf{cuisine}, \textbf{le prix} , \textbf{l'ambiance} et \textbf{la localisation} pour le choix du restaurant. Par exemple le restaurant Barocco est défini avec les critères présenté dans la table \ref{teb:exfr}.
			\begin{table}[h]
				\begin{tabular} {|c|c|c|c|c|}
					\hline
					Nom du restaurant & cuisine & prix & ambiance& localisation \\
					\hline
					Borocco & Italien & Grande table & Calme & à coté de la rivière \\
					\hline 
				\end{tabular}
				\label{teb:exfr}
				\caption{Présentation du restaurant Borocco}
			\end{table}
			
			L'étude se déroulera en trois étapes:
			
			Premièrement, vous allez effectuer une session d'entraînement afin de vous familiariser avec l'interface d'interaction.
			
			Ensuite, pour les besoins de l'étude, nous vous demanderons de renseigner vos préférences par critères. Les agents avec qui vous allez dialoguer ne connaissent pas vos préférences. Les informations sur vos préférences seront utilisées pour analyser les dialogues. Merci de bien vouloir respecter les préférences renseigné dans vos interactions.
			
			Finalement, vous allez discuter avec trois personnes différentes représentées par des agents conversationnels.  Comportez vous \textbf{naturellement} avec chacun des trois agents, comme vous l'auriez fait avec une de vos connaissance pour choisir un restaurant.  
			
			
			Si vous avez des questions, c'est le moment de les poser à l'expérimentateur. Sinon, nous allons commencer la phase d'entraînement 
			\textcolor{blue}{Ici se termine le texte de présentation et nous pouvons lancer la partie tutoriel avec la présence de l'expérimentateur pour toute explication}.
			
			\subsubsection{Phase tutoriel}
			Dans le cadre de cette étude, vous allez interagir avec l'agent via une interface qui vous permettra de sélectionner des actes dialogiques pour négocier. 
			Chaque acte de dialogue permet de générer automatiquement une phrase correspondant a ce que vous voulez exprimer.
			Montrer un exemple de sélection. Expliquer les notions de critères et options. Ensuite laisser la main à l'utilisateur pour choisir des actes.  
			
			
			
			\textcolor{red}{Remarque générale : tu ne dis pas trop à quoi va ressembler l'interaction. Je pense qu'il faudrait expliquer (choisir des types de phrase, on voit la phrase, etc). Comme tu tu rédigeais un "tuto" sur l'utilisation de l'interface d'Hatem. }
			
				\subsection{Reseignement des préférences}
				\subsubsection{Ecran d'acceuil}
				
				\textbf{Version FR}
				
					
					Pour les besoin de l'étude, nous vous demandons de bien vouloir renseigner vos préférences pour chaque critère sur lesquels portera la négociation.
				
					Nous vous invitons à classer les valeurs \textbf{ant}e vos préférences, en commençant par la valeur qui vous aimez le plus 	Si vous avez des questions, c'est le moment de les poser à l'expérimentateur. Sinon, nous allons commencer l'étude.
				

			
					
					\subsubsection{Pour chaque critère}
					Toutes choses égales par ailleurs, classez par ordre croissant de vos préférences les valeurs suivantes: 
		\subsection{Questionnaire}		
		\begin{enumerate}
			% We need to evaluate the perception of the value creation 
			\item Je suis satisfait avec le choix final
			\item Le choix final était juste pour l'agent
			
			% manipulation check question
			\item La cuisine était le premier critère sur lequel vous vous êtes mis d'accord 
			\item  Nous nous sommes mi d'accord pour aller à un restaurant gastronomique.
			% Evaluate the liking during the negotiation
			\item J'ai aimé négocier avec l'agent
			
			
			% Evaluate the compfort in the negotiation
			\item Je me suis senti à l'aise pendant le processus de négociation.
			\item J'ai trouvé que l'interaction était confortable
			\item Je me sentais détendu pendant la négociation
			\item Je me sentais anxieux pendant la négociation
			
			
			% Evaluate behaviors of dominance during the negotiation
			\item L'agent a pris en compte mes préférences.
			\item L'agent a maintenu sa position durant la négociation.
			\item L'agent renonce à sa position durant la négociation.
			\item L'agent a fait des concessions durant la négociation
			\item L'agent a pris les rênes de la négociation.(L'agent jouait le rôle de leader dans la négociation)
			\item L'agent était égocentrique.
			\item L'agent a pris l'initiative de la négociation.
			\item L'agent était exigeant
			
			
			
			\item J'avais tendence à prendre les rênes durant la négociation.
			\item J'ai pris en compte les préférences de l'agent.
			\item J'ai abondonné ma position durant la négociation
			\item J'ai maintenu ma position durant la négociation.
			\item J'étais égocentrique durant la négociation.
			\item J'ai fait des concessions pendant la négociation.	
			\item J'ai pris l'initiative lors de la négociation
			\item J'étais exigeant
			
			
			
		\end{enumerate}	
					
	\end{document}